% Bibliographie

\begin{frame}[c]
  \frametitle{Contributions personnelles}

\small
Chapitre de livre :
\begin{itemize}
  \item Loïc Paulevé, Courtney Chancellor, \emphcolor{Maxime Folschette}, Morgan Magnin et Olivier Roux :
    \emphcolor{Analyzing Large Network Dynamics with Process Hitting},
    \textit{Logical Modeling of Biological Systems},
    éditeurs : Luis Farinas del Cerro et Katsumi Inoue,
    août 2014, ISBN 978-1-84821-680-8.
\end{itemize}

\medskip
Conférences et workshops :
\begin{itemize}
  \item \emphcolor{Maxime Folschette}, Loïc Paulevé, Morgan Magnin et Olivier Roux :
    \emphcolor{Under-approximation of reachability in multivalued asynchronous networks},
    in: Proceedings of the fourth International Workshop on Interactions between Computer Science and Biology, éditeurs : Emanuela Merelli et Angelo Troina,
    \textit{Electronic Notes in Theoretical Computer Science}, \vol 299,
    33--51, Springer Berlin Heidelberg, juin 2013, DOI 10.1016/j.entcs.2013.11.004.
    %\emphcolor{Selected for a special issue in the journal \textit{Theoretical Computer Science}.}
  \item \emphcolor{Maxime Folschette}, Loïc Paulevé, Katsumi Inoue, Morgan Magnin et Olivier Roux :
    \emphcolor{Concretizing the process hitting into biological regulatory networks}, %\newline{}
    in: \textit{Computational Methods in Systems Biology}, éditeurs : David Gilbert et Monika Heiner, %\newline{}
    166--186, Springer Berlin Heidelberg, octobre 2012, DOI 10.1007/978-3-642-33636-2\_11.
  \item \emphcolor{Maxime Folschette}, Loïc Paulevé, Katsumi Inoue, Morgan Magnin et Olivier Roux :
    \emphcolor{Abducing Biological Regulatory Networks from Process Hitting models},
    in: \textit{ECML-PKDD 2012 Workshop on Learning and Discovery in Symbolic Systems Biology}, éditeurs : Oliver Ray et Katsumi Inoue,
    24--35, septembre 2012.
\end{itemize}

\end{frame}



\begin{frame}[c]
  \frametitle{Bibliography}

%\footnotesize
\small
\setlength{\parindent}{-1em}
\setlength{\parskip}{0.5em}

\tcitebullet Loïc Paulevé, Morgan Magnin, Olivier Roux. \ex{Refining dynamics of gene regulatory networks in a stochastic $\pi$-calculus framework}. In Corrado Priami, Ralph-Johan Back, Ion Petre, and Erik de Vink, editors: \textit{Transactions on Computational Systems Biology XIII}, volume 6575 of Lecture Notes in Computer Science, pages 171--191, 2011.

\tcitebullet Loïc Paulevé, Morgan Magnin, Olivier Roux. \ex{Static analysis of biological regulatory networks dynamics using abstract interpretation}. \textit{Mathematical Structures in Computer Science}, 2012.

%\tcitebullet Adrien Richard, Jean-Paul Comet, Gilles Bernot. \ex{R. Thomas' logical method}, 2008. Invited at \textit{Tutorials on modelling methods and tools: Modelling a genetic switch and Metabolic Networks}, Spring School on Modelling Complex Biological Systems in the Context of Genomics.

%\tcitebullet Adrien Richard, Jean-Paul Comet, Gilles Bernot. \textit{Modern Formal Methods and App.}, chapter \ex{Formal Methods for Modeling Biological Regulatory Networks}, pages 83--122, 2006.

%\tcitebullet Maxime Folschette, Loïc Paulevé, Katsumi Inoue, Morgan Magnin, Olivier Roux. \ex{Concretizing the Process Hitting into Biological Regulatory Networks}. In David Gilbert and Monika Heiner, editors, \textit{Computational Methods in Systems Biology X}, Lecture Notes in Computer Science, pages 166--186. Springer Berlin Heidelberg, 2012.

\tcitebullet Maxime Folschette, Loïc Paulevé, Morgan Magnin, Olivier Roux. \ex{Under-approximation of Reachability in Multivalued Asynchronous Networks}. In E. Merelli and A. Troina, editors, \textit{4th International Workshop on Interactions between Computer Science and Biology (CS2Bio’13)}, Electronic Notes in Theoretical Computer Science, Volume 299, 33–51. June 2013.

\tcitebullet Loïc Paulevé. PhD thesis: \ex{\textit{Modélisation, Simulation et Vérification des Grands Réseaux de Régulation Biologique}}, October 2011, Nantes, France.

%\tcitebullet Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Tuning Temporal Features within the Stochastic $\pi$-Calculus}. IEEE Transactions on Software Engineering, 37(6), pages 858--871, 2011.

%\tcitebullet Loïc Paulevé and Adrien Richard. \textit{Topological Fixed Points in Boolean Networks}. Comptes Rendus de l'Académie des Sciences - Series I - Mathematics, 348(15-16), pages 825--828, 2010.

%\tcitebullet Gilles Bernot, Franck Cassez, Jean-Paul Comet, Franck Delaplace, Céline Müller, Olivier Roux. \ex{Semantics of Biological Regulatory Networks}. \textit{Proceedings of the First Workshop on Concurrent Models in Molecular Biology}, Electronic Notes in Theoretical Computer Science 180(3), pages 3--14, 2007.

%\tcitebullet Adrien Richard. \ex{Negative circuits and sustained oscillations in asynchronous automata networks}. \textit{Advances in Applied Mathematics} 44(4), pages 378--392, 2010.

\tcitebullet Paul François, Vincent Hakim, Eric D Siggia. \ex{Deriving structure from evolution : metazoan segmentation}.
In \textit{Molecular Systems Biology}, Volume 3, Issue 1. 2007.

\end{frame}
